What do they see? Testing perceptual accuracy in a U.S. general population survey using stacked bar charts

### 2023-10-26 revisions-round1/response-to-reviewers.qmd

---
title: "Round 1: Response to Reviewers"
format: pdf
editor: source
---

## Reviewer 1

-   The introduction doesn't provide a clear rationale for the questions' importance.

    -   *In response to specific comments from Reviewer 2, we have strengthened some of the wording in the introduction to better emphasize the importance of our work and the survey framework. We hope this addresses this concern.*

-   The entire article reads more like a project report rather than a scientific paper, with an excess of questions and bullet-pointed sentences.

    -   *To address this, we have removed two of the instances of bulleted lists: one which listed out the three variations in testing, each described in a bullet, and a second which demonstrated the options participants have to select from, each option shown in a bullet. The third list, which we have kept intact, is a list of the three research questions we pose to answer through our study. The authors could not identify a reason to remove the list structure for our research questions, as it clearly separates each of the distinct questions for the reader. There are four questions in the text of the paper: one at the very beginning, posing the question 'What do viewers see when we show them a data chart?', and three associated with the research questions. We have not removed any of these, as a question mark at the end of a research question is appropriate, and posing an opening question in the introduction is also appropriate.*

@@

    -   *Per AE and Editor, we are not responding to this comment.*

## Reviewer 2

-   Major comments

    -   The title, abstract and conclusion suggests a wider context but the content is actually more limited in scope. I suggest changing the title to emphasise the main points in the article: 1) nationally representative sample and 2) testing stacked barplots. I think statements like "Our study results provide actionable insights that data visualization practitioners can utilize in the design of data visualizations." extrapolates too much. It should be more specific in that the actionable insights is *for stacked barplots* and also write concretely what the recommendation is (i.e., vertical display, align groups that most important to compare, etc.).
        -   *We have updated the statement in the conclusions per a specific recommendation in the minor comments. In addition, we have updated the paper title and some of the language in the abstract to reflect that the scope is limited to testing stacked bar charts. We have also updated the recommendation language in the conclusions to be more concretely focused on stacked bar charts.*

@@

    -   Do the authors have recommendations for (non-representative) visualisation perception surveys given their experience on nationally representative sample? E.g. given that the surveys conducted via Mturks etc are biased toward highly educated young males and authors found differences between the income group, what do these non-representative survey inform us?
        -   *We have added the following text to our conclusions to address this point: "If studies using non-representative or crowd-sourced samples find non-significant results when studying elements of design, those results may not actually be non-significant for other populations, particularly lower education or lower income populations. Researchers should not disregard non-significant findings in those survey studies but rather ask whether the lack of significance would hold across population subgroups."*

-   Minor comments

    -   I think the paper can benefit in the intro to include a stronger emphasis why we want to achieve a representative sample. The authors do address this in part but it reads like an aside ("..., a common target audience for data visualisation"). Maybe a paragraph on about how data visualisation is used by general public (e.g. results on polls in the news -- this can also lead to why the authors chose to focus on barplots too as polls are often count data). Authors can also discuss how it is *imperative to be inclusive* as these data visualisation can be informative and the results need to be accessible by the *whole* population and not just the elite/highly educated population (which seem to be the bias towards at lot of these surveys have). I think also a stronger emphasis on the importance of the authors' works is needed, e.g., "this is the first study to ...". Also in conclusion, the authors state "The size of our sample aids in identifying this signal.", but the authors can instead state e.g. "our study is orders of magnitude larger than other studies with similar scope, demonstrating...".
        -   *There are multiple points here; we will address each.*
        -   Stronger emphasis on why we want to achieve a representative sample
            -   *We have added additional language in the introduction emphasizing the point of the general public as a target audience and the importance of using a representative survey population. We added the following language: "The general public is a common target audience for data visualization and scientific communication work; results of polls, surveys, and scientific work are presented often in the news, shared on social media, or posted online or in print materials. It is imperative that data visualizations used to communicate these topics are designed with the goal of reaching the entire population. To that end, an inclusive, representative approach to studying how viewers perceive information presented in charts is critical to understand how best to communicate with the general public".*
        -   Stronger emphasis on the importance of the authors' work is needed
            -   *Some of this has been addressed with the changes in the prior comment; however, we also updated the language in the conclusions to mention the large sample size relative to prior work. Further, in response to another comment, we expanded on the impact our findings have for interpreting non-representative studies, which we hope further underscores the importance of our work.*

    -   While I think the content is fine, I think the grammar in the paper can be better polished. (It is not that the current grammar is bad, but I just think it can be improved to make this a better paper). I have outlined some of the suggested corrections below.

@@

-   The AE and I do believe this is within the scope for this special issue, contrary to the final comment from Referee #1, so no need to address that comment.

-   **Please add an unnumbered section Supplementary Material to list its content (e.g., data, code, additional simulation results, technical proofs, etc.). See recently published papers for examples. Reproducibility is held high at the JDS; the reproducibility team will check for reproducibility when the paper is accepted.**

-   When addressing the comments, please keep in mind that there is a 20-page limit (including everything) in the production style.

-   In general, both reviewers express some concerns regarding some of the language and description regarding overall impact of the work. I would encourage the authors to make it more clear that their primary contribution is in using a representative probability sample, and that their conclusions are focused on stacked barplot displays, as Reviewer 2 specifically remarks, and highlight why conclusions from a non-representative sample may be problematic within the data visualization world.

    -   *We have updated the language in the title, abstract, introduction, and conclusion to be responsive to these concerns. See our specific responses to Reviewer 2's specific comments, but in general we added more emphasis on the importance of communicating a general audience, why non-representative survey findings don't necessarily hold for the entire population, and clarified that our scope was specifically on stacked bar chart displays.*

@@

-   **I believe the figures are fairly clear (per Reviewer 1's comment), but the authors might also be inclined to be more selective with what is shown in Figures 3, 6-8, and maybe move some of the others to an appendix.**

-   Can the authors comment further on modeling assumptions, particularly in relation to presenting all participants with the unaligned plot first followed by the aligned plot second (as opposed to randomizing this)? For instance, perhaps some participants notice that the plots are the same, with just the bars stacked in a different order, and their response to the second task is biased to be equivalent to that of the first task. This seems like it would be more of a problem if the plots were presented in the reverse order, but I'm curious if the authors looked into this.

    -   *We acknowledge that this is a limitation. There is a chance that someone recognizes they are completing the same task with the same bars when we present the aligned task before the unaligned task; we made the assumption that the chance of recognizing the tasks is lower when seeing unaligned prior to aligned. Participants are not able to return to the prior question once they move on to the second question, which does make it more difficult for participants to compare the tasks to one another. We also added the following text in the section describing alignment: "Participants first saw the chart with the unaligned comparison, followed by the chart with the aligned comparison, but could not return to the first comparison after completing it. While there is some risk of participants recognizing the subsequent tasks to be the same value comparisons, the unaligned (harder) task was shown first to reduce the likelihood of participants carrying over an answer from the aligned (easier) task."*

@@

-   **Is there a reason why the meaning/values of i from 1 to 3 are reversed between the two models specified in Equations 4 and 7?**

    -   KR: **Heike, please confirm** which order they should be in.

-   It appears the cumulative logistic regression model with respect to participant demographic covariates just considers first-order effects, but interactions would also be pretty interesting here. Are there any notable interaction effects?

    -   *While we agree interactions would be interesting here, we lose sample size pretty quickly when interacting across demographic groups, particularly for demographics with several categories (e.g., education level and race/ethnicity). We are not comfortable with completing inference with those sample sizes, particularly given how important properly representing the relationship of demographic characteristics to outcomes is to our work. However, this is precisely the reason we hope to complete surveys with larger sample sizes, and possibly oversamples for underrepresented groups, in the future; studying those interactions could provide valuable insight into how subgroups in the general population interact with charts.*

-   The letter notation used to denote significance is a bit confusing to me (e.g., Figure 5, Table 3), can the authors clarify this within the text or modify accordingly? What do a, b, c, etc. actually mean? If this is convention from Piepho (2004), it would be useful for this to be explained more or changed for a more general audience.

    -   *We have expanded the discussion on the interpretation of connected letters, and included an example for their first use.*

### 2023-10-26 SDSS-2023/testing-charts-accuracy.qmd
additional language updates to respond to R1, R2, and editor comments.

Cleveland and McGill's work -- while a foundational user study in graphical perception -- utilized a small convenience sample, consisting of only a few individuals recruited from among the authors' coworkers and their spouses.
@heerCrowdsourcingGraphicalPerception2010 reproduced Cleveland and McGill's rankings using a larger sample from a crowd sourcing platform, employing a total of 82 Amazon Mechanical Turk (mTurk) workers for the study.
Crowd sourced samples were shown by @borgoCrowdsourcingInformationVisualization2017 to be biased towards more male, younger, and relatively well-educated individuals relative to the adult U.S. population as a whole; generally, convenience and opt-in samples are not representative of the general population, a common target audience for data visualization and scientific communication work.
Further, higher education individuals are likely to have prior exposure to data visualization or data topics in higher education, which may not be the case for other groups within the population; existing differences in exposure to data may drive differences in results across groups.

@@

We would expect that comparing unaligned tiles is a harder task (with correspondingly lower levels of accuracy) than a comparison of aligned tiles, with the framing given by the other tiles in the same column mitigating some of this difficulty.
In particular, the additional context of the other tiles should *help* rather than *hurt* the comparison, unlike other situations, where additional information besides the pieces involved in the comparison were found to be distractors [@talbotFourExperimentsPerception2014].

@@

```{r}
#| label: fig-rounds-demographics
#| fig-cap: "Overview of participants' demographics in each of the tasks: the colored dots show marginal percentages for demographics across the three tasks. In comparison, the dark lines show upper and lower 95% confidence of these demographics as estimated by the American Community Survery (ACS) 2021. Note that for a lot of these intervals the estimates are so close together that they appear as a single line. "
#| fig-height: 7
#| fig-width: 12

@@

rounds_col <- RColorBrewer::brewer.pal(name="Accent", n=8)[c(1,3,5)]
#[1] "#7FC97F" "#BEAED4" "#FDC086" "#FFFF99" "#386CB0" "#F0027F" "#BF5B17" "#666666"
gender <- acs_gender %>%
  ggplot(aes(x = gender)) +
  geom_errorbar(aes(ymin = percent-moe_percent, ymax=percent+moe_percent, colour="ACS estimate")) +
#  geom_point(aes(y = percent)) +
  geom_point(
    size=3,
    aes(x = sex, y = value, colour=chart),
    position = position_dodge(width = 0.5),
    data = omni_gender %>% filter(group=="mean")
  ) +
  ylim(c(0, NA)) +
  geom_linerange(
    aes(
      x = sex,
      ymin = low,
      ymax=high,
      colour=chart
    ),
    linewidth = 1, 
    position = position_dodge(width = 0.5),
    data = omni_gender %>% pivot_wider(names_from=group, values_from=value),
    show.legend = FALSE
  ) +
  ylab("Percent") + 
  ggtitle("Gender") +
#  theme(axis.text.x = element_text(angle=0, vjust = 0.5)) +
  xlab("") +
#  theme(legend.position ="none") +
  scale_linetype_manual(values=c(2,2,1)) +
  scale_color_manual(values=c("grey20", rounds_col))

acs_age <- data.frame(age4 = c("18-29", "30-44", "45-59", "60+"), 
                      estimate = c(22854328 + 30339089, 
                                   22506614 + 21920290 + 20521593, 
                                   20582187 + 21049271 + 21928936, 
                                   73789098),
                      percent = c(6.9 + 9.2, 
                                  6.8 + 6.6 + 6.2, 
                                  6.2 + 6.4 + 6.7, 
                                  22.4
                                  ),
                      moe_percent = c(sqrt(0.1^2+0.1^2),
                              sqrt(0.1^2+0.1^2 + 0.1^2),
                              sqrt(0.1^2+0.1^2 + 0.1^2),
                              0.1) )
acs_age <- acs_age %>% mutate(percent2 = estimate/sum(estimate)*100)

@@

age_bak <- round_123 %>% 
  ggplot(aes(x = age4)) + 
  geom_bar(aes(weight = weight_pct_round), fill="grey", colour = "grey30", linewidth=0.5) + 
  ylab("Percent") + 
  ggtitle("Age ") +
  theme(axis.text.x = element_text(angle=30, hjust = 1)) +
  xlab("") + ylim(c(0,40)) +
  facet_grid(.~chart) +
  geom_point(aes(x = age4, y = percent), data = acs_age) +
  geom_segment(
    aes(
      x = as.numeric(age) - 0.45,
      y = value,
      xend = as.numeric(age) + 0.45,
      yend = value,
      linetype=group
    ), 
    alpha = 1, colour = "black", linewidth = 0.25,
    data = omni_age
  )  +
  scale_linetype_manual(values=c(2,2,1)) +
  theme(legend.position = "none")

age <- acs_age %>%
  ggplot(aes(x = age4)) +
  geom_errorbar(aes(ymin = percent2-moe_percent, ymax=percent2+moe_percent, colour="ACS estimate")) +
#  geom_point(aes(y = percent)) +
  geom_point(
    size=3,
    aes(x = age, y = value, colour=chart),
    position = position_dodge(width = 0.5),
    data = omni_age %>% filter(group=="mean")
  ) +
  ylim(c(0, NA)) +
  geom_linerange(
    aes(
      x = age,
      ymin = low,
      ymax=high,
      colour=chart
    ),
    linewidth = 1,
    position = position_dodge(width = 0.5),
    data = omni_age %>% pivot_wider(names_from=group, values_from=value)
  ) +
  ylab("Percent") + 
  ggtitle("Age groups") +
  theme(axis.text.x = element_text(angle=0, vjust = 0.5)) +
  xlab("") +
  theme(legend.position ="none") +
  scale_linetype_manual(values=c(2,2,1)) +
  scale_color_manual(values=c("grey20", rounds_col))

acs_educ5 <- data.frame(educ5 = c("Less than HS", "HS or equivalent", "Some college",  "Bachelor", "Post graduate"), 
                      estimate = c(
                      3636691 + 10793507 + 14256849, 
                      9974372 + 59636386,
                      13050667 + 45042031 + 19614710,
                      3677359 + 46354331,
                      29454503),
                      moe_percent = c(sqrt(0.1^2+0.1^2+0.1^2),
                              sqrt(0.1^2+0.1^2 ),
                              sqrt(0.1^2+0.1^2 + 0.1^2),
                              sqrt(0.1^2+0.2^2 ),
                              0.1) 
                      )
acs_educ5 <- acs_educ5 %>% mutate(percent = estimate/(30339089+225152317)*100)

@@

education_bak <- round_123 %>% 
  ggplot(aes(x = educ5)) + 
  geom_bar(aes(weight = weight_pct_round), fill="grey", colour = "grey30", linewidth=0.5) + 
  ylab("Percent") + 
  ggtitle("Education levels") +
  theme(axis.text.x = element_text(angle=30, hjust = 1)) +
  xlab("") + ylim(c(0,40)) +
  facet_grid(.~chart) +
  geom_point(aes(y = percent), data = acs_educ5) +
  geom_segment(
    aes(
      x = as.numeric(educ) - 0.45,
      y = value,
      xend = as.numeric(educ) + 0.45,
      yend = value,
      linetype=group
    ), 
    alpha = 1, colour = "black", linewidth = 0.25,
    data = omni_educ
  )  +
  scale_linetype_manual(values=c(2,2,1)) +
  theme(legend.position = "none")

education <- acs_educ5 %>%
  mutate(educ5 = factor(educ5, levels=levels(omni_educ$educ))) %>%
  ggplot(aes(x = educ5)) +
  geom_errorbar(aes(ymin = percent-moe_percent, ymax=percent+moe_percent, colour="ACS estimate")) +
#  geom_point(aes(y = percent)) +
  geom_point(
    size=3,
    aes(x = educ, y = value, colour=chart),
    position = position_dodge(width = 0.5),
    data = omni_educ %>% filter(group=="mean")
  ) +
  ylim(c(0, NA)) +
  geom_linerange(
    aes(
      x = educ,
      ymin = low,
      ymax=high,
      colour=chart
    ),
    linewidth = 1, 
    position = position_dodge(width = 0.5),
    data = omni_educ %>% pivot_wider(names_from=group, values_from=value),
    show.legend = FALSE
  ) +
  ylab("Percent") + 
  ggtitle("Education") +
#  theme(axis.text.x = element_text(angle=0, vjust = 0.5)) +
  xlab("") +
  theme(legend.position ="none") +
  scale_linetype_manual(values=c(2,2,1)) +
  scale_color_manual(values=c("grey20", rounds_col))

acs_income <- data.frame(
  income4 = c("< $30k", "$30k - $60k", 
              "$60k - $100k", "more than $100k"), 
  percent = c(6+3.9+7.5+ .5*7.8, 
              .5*7.8 + 11.3 + .4*16.8, 
              .6*16.8+12.8,
              16.3+7.9+9.8),
  moe_percent = c(sqrt(0.1^2+0.1^2+0.1^2+0.1^2+0.1^2),
                  sqrt(0.1^2+0.1^2+0.1^2),
                  sqrt(0.1^2 + 0.1^2),
                  sqrt(0.1^2+0.1^2+0.1^2))
  )

@@

income_bak <- round_123 %>% 
  ggplot(aes(x = income4)) + 
  geom_bar(aes(weight = weight_pct_round), fill="grey", colour = "grey30", linewidth=0.5) + 
  ylab("Percent") + 
  ggtitle("Income levels (Family)") +
  theme(axis.text.x = element_text(angle=30, hjust = 1)) +
  xlab("") + ylim(c(0,40)) +
  facet_grid(.~chart) +
  geom_point(aes(y = percent), data = acs_income) +
  geom_segment(
    aes(
      x = as.numeric(income) - 0.45,
      y = value,
      xend = as.numeric(income) + 0.45,
      yend = value,
      linetype=group
    ), 
    alpha = 1, colour = "black", linewidth = 0.25,
    data = omni_income
  )  +
  scale_linetype_manual(values=c(2,2,1)) +
  theme(legend.position = "none")

income <- acs_income %>%
  mutate(income4 = factor(income4, levels=levels(omni_income$income))) %>%
  ggplot(aes(x = income4)) +
  geom_errorbar(aes(ymin = percent-moe_percent, ymax=percent+moe_percent, colour="ACS estimate")) +
#  geom_point(aes(y = percent)) +
  geom_point(
    size=3,
    aes(x = income, y = value, colour=chart),
    position = position_dodge(width = 0.5),
    data = omni_income %>% filter(group=="mean")
  ) +
  ylim(c(0, NA)) +
  geom_linerange(
    aes(
      x = income,
      ymin = low,
      ymax=high,
      colour=chart
    ),
    linewidth = 1, 
    position = position_dodge(width = 0.5),
    data = omni_income %>% pivot_wider(names_from=group, values_from=value),
    show.legend = FALSE
  ) +
  ylab("Percent") + 
  ggtitle("Income") +
#  theme(axis.text.x = element_text(angle=0, vjust = 0.5)) +
  xlab("") +
  theme(legend.position ="none") +
  scale_linetype_manual(values=c(2,2,1)) +
  scale_color_manual(values=c("grey20", rounds_col))

@@

With our survey framework, we have shown that we can rank structural variations on design and tasks by their relative accuracy; we identified significantly different rates of respondent accuracy under different designs presenting the same data.
The size of our sample aids in identifying this signal.

>>>>

Cleveland and McGill's work -- while a foundational user study in graphical perception -- utilized a small convenience sample, consisting of only a few individuals recruited from among the authors' coworkers and their spouses.
@heerCrowdsourcingGraphicalPerception2010 reproduced Cleveland and McGill's rankings using a larger sample from a crowd sourcing platform, employing a total of 82 Amazon Mechanical Turk (mTurk) workers for the study.
Crowd sourced samples were shown by @borgoCrowdsourcingInformationVisualization2017 to be biased towards more male, younger, and relatively well-educated individuals relative to the adult U.S. population as a whole; generally, convenience and opt-in samples are not representative of the general population.
Further, higher education individuals are likely to have prior exposure to data visualization or data topics in higher education, which may not be the case for other groups within the population; existing differences in exposure to data may drive differences in results across groups. The general public is a common target audience for data visualization and scientific communication work; results of polls, surveys, and scientific work are presented often in the news, shared on social media, or posted online or in print materials. It is imperative that data visualizations used to communicate these topics are designed with the goal of reaching the entire population. To that end, an inclusive, representative approach to studying how viewers perceive information presented in charts is critical to understand how best to communicate with the general public.

@@

We would expect that comparing unaligned tiles is a harder task (with correspondingly lower levels of accuracy) than a comparison of aligned tiles, with the framing given by the other tiles in the same column mitigating some of this difficulty.
In particular, the additional context of the other tiles should *help* rather than *hurt* the comparison, unlike other situations, where additional information besides the pieces involved in the comparison were found to be distractors [@talbotFourExperimentsPerception2014]. Participants first saw the chart with the unaligned comparison, followed by the chart with the aligned comparison, but could not return to the first comparison after completing it. While there is some risk of participants recognizing the subsequent tasks to be the same value comparisons, the unaligned (harder) task was shown first to reduce the likelihood of participants carrying over an answer from the aligned (easier) task.

@@

```{r}
#| label: fig-rounds-demographics
#| fig-cap: "Demographics of respondents in each of the tasks. The dots show percentages of the national demographics as estimated by the American Community Survery (ACS) 2021."
#| fig-height: 7
#| fig-width: 12

@@

gender <- acs_gender %>%
  ggplot(aes(x = gender)) +
  geom_errorbar(aes(ymin = percent-moe_percent, ymax=percent+moe_percent)) +
  geom_point(aes(y = percent)) +
  geom_point(
    aes(x = sex, y = value, colour=chart),
    position = position_dodge(width = 0.5),
    data = omni_gender %>% filter(group=="mean")
  ) +
  geom_linerange(
    aes(
      x = sex,
      ymin = low,
      ymax=high,
      colour=chart
    ),
    position = position_dodge(width = 0.5),
    data = omni_gender %>% pivot_wider(names_from=group, values_from=value)
  )

acs_age <- data.frame(age4 = c("18-29", "30-44", "45-59", "60+"), 
                      estimate = c(22854328 + 30339089, 
                                   22506614 + 21920290 + 20521593, 
                                   20582187 + 21049271 + 21928936, 
                                   73789098))
acs_age <- acs_age %>% mutate(percent = estimate/sum(estimate)*100)

@@

age <- round_123 %>% 
  ggplot(aes(x = age4)) + 
  geom_bar(aes(weight = weight_pct_round), fill="grey", colour = "grey30", linewidth=0.5) + 
  ylab("Percent") + 
  ggtitle("Age ") +
  theme(axis.text.x = element_text(angle=30, hjust = 1)) +
  xlab("") + ylim(c(0,40)) +
  facet_grid(.~chart) +
  geom_point(aes(x = age4, y = percent), data = acs_age) +
  geom_segment(
    aes(
      x = as.numeric(age) - 0.45,
      y = value,
      xend = as.numeric(age) + 0.45,
      yend = value,
      linetype=group
    ), 
    alpha = 1, colour = "black", linewidth = 0.25,
    data = omni_age
  )  +
  scale_linetype_manual(values=c(2,2,1)) +
  theme(legend.position = "none")

acs_educ5 <- data.frame(educ5 = c("Less than HS", "HS or equivalent", "Some college",  "Bachelor", "Post graduate"), 
                      estimate = c(28687047, 69610758, 77707408, 50031690, 29454503))
acs_educ5 <- acs_educ5 %>% mutate(percent = estimate/sum(estimate)*100)

@@

education <- round_123 %>% 
  ggplot(aes(x = educ5)) + 
  geom_bar(aes(weight = weight_pct_round), fill="grey", colour = "grey30", linewidth=0.5) + 
  ylab("Percent") + 
  ggtitle("Education levels") +
  theme(axis.text.x = element_text(angle=30, hjust = 1)) +
  xlab("") + ylim(c(0,40)) +
  facet_grid(.~chart) +
  geom_point(aes(y = percent), data = acs_educ5) +
  geom_segment(
    aes(
      x = as.numeric(educ) - 0.45,
      y = value,
      xend = as.numeric(educ) + 0.45,
      yend = value,
      linetype=group
    ), 
    alpha = 1, colour = "black", linewidth = 0.25,
    data = omni_educ
  )  +
  scale_linetype_manual(values=c(2,2,1)) +
  theme(legend.position = "none")

acs_income <- data.frame(
  income4 = c("< $30k", "$30k - $60k", 
              "$60k - $100k", "more than $100k"), 
  percent = c(6+3.9+7.5+ .5*7.8, 
              .5*7.8 + 11.3 + .4*16.8, 
              .6*16.8+12.8,
              16.3+7.9+9.8))

@@

income <- round_123 %>% 
  ggplot(aes(x = income4)) + 
  geom_bar(aes(weight = weight_pct_round), fill="grey", colour = "grey30", linewidth=0.5) + 
  ylab("Percent") + 
  ggtitle("Income levels (Family)") +
  theme(axis.text.x = element_text(angle=30, hjust = 1)) +
  xlab("") + ylim(c(0,40)) +
  facet_grid(.~chart) +
  geom_point(aes(y = percent), data = acs_income) +
  geom_segment(
    aes(
      x = as.numeric(income) - 0.45,
      y = value,
      xend = as.numeric(income) + 0.45,
      yend = value,
      linetype=group
    ), 
    alpha = 1, colour = "black", linewidth = 0.25,
    data = omni_income
  )  +
  scale_linetype_manual(values=c(2,2,1)) +
  theme(legend.position = "none")

@@

With our survey framework, we have shown that we can rank structural variations on design and tasks by their relative accuracy; we identified significantly different rates of respondent accuracy under different designs presenting the same data.
Our study sample is larger than prior studies with a similar scope. That large sample size improves our power to identify this signal.
